Project Report\\\textsc{DEVS Ex Machina}

### 2015-04-25 manual/projectrapport.tex
* removed tracerID from the tracemessage * write the Tracer part of the report in a separate file so that it doesn't clutter the main file. (the thing is 7 pages long!) - - -> the main file contains a link to this second report - - -> If you want to, I can always include this file in the main report. I just thought that this was cleaner
Missing commandline in rapport.
Project report: added serialization

\section{Serialization}
For serialization we used the Cereal \cite{cereal} header only framework.
%TODO Pieter

>>>>

\section{Serialization}
For serialization we used the Cereal \cite{cereal} header-only framework. We have used separate load and save functions for full flexibility. For each type that occurs in the form of a pointer we implemented a static load and construct function since the object first has to be created before the saved data can be imported. Cereal has a small coupling with the code (models) that has to be written by the user as the user has to register his own classes due to polymorphism.
